### 2011-07-28 doc/theses/svirec/kap3.tex
another changes

As was mentioned earlier, a repairing primitive is a node value modification, where for repairing algorithm a combination of two rules to resolve violation is used. Let us have an $FD$ $\sigma = (P, P', (P_1, \dots, P_n \rightarrow P_{n+1}))$ (from definition \ref{fd2}) and consider two nodes $v_1$ and $v_2$ matching path $P'$ in a subtree rooted at a node in $\{[\![p]\!]\}$. If the child nodes of $v_1$ and $v_2$ qualified by paths $P_i$ have equal values for all $i \in [1,n]$ and their child nodes qualified by $P_{n+1}$ have different values, then $v_1$ and $v_2$ violates $\sigma$. The first rule used to repair this violation is to change the value of the node qualified by $P_{n+1}$ from $v_1$ to the value of $v_2$'s child node that matches $P_{n+1}$ (or reversely). The second rule is to choose an arbitrary $P_i (i \in [1,n])$ and introduce a new value to the node qualified by $P_i$ from $v_1$ (or $v_2$).

>>>>

As was mentioned earlier, a repairing primitive is a node value modification, where for repairing algorithm a combination of two rules to resolve violation is used. Let us have an $FD$ $\sigma = (P, P', (P_1, \dots, P_n \rightarrow P_{n+1}))$ (from Definition \ref{fd2}) and consider two nodes $v_1$ and $v_2$ matching path $P'$ in a subtree rooted at a node in $\{[\![p]\!]\}$. If the child nodes of $v_1$ and $v_2$ qualified by paths $P_i$ have equal values for all $i \in [1,n]$ and their child nodes qualified by $P_{n+1}$ have different values, then $v_1$ and $v_2$ violates $\sigma$. The first rule used to repair this violation is to change the value of the node qualified by $P_{n+1}$ from $v_1$ to the value of $v_2$'s child node that matches $P_{n+1}$ (or reversely). The second rule is to choose an arbitrary $P_i (i \in [1,n])$ and introduce a new value to the node qualified by $P_i$ from $v_1$ (or $v_2$).
